The Impact of Subway Systems on Air Pollution

### 2023-02-24 Paper Two .qmd
new

## Analysis Tool
The data will be presented clearly and succinctly with these visuals, making it simpler to comprehend the relation between air pollution and subway. This following analysis is processed in R (@R) with packages of tidyverse(@tidyverse), dplyr(@dplyr). The tables is constructed via knitr(@knite). The package inside of tidyverse helps to create the plots via ggplot2(@tidyverse). This paper is knitted as PDF file by the packages of R markdown (@RMarkdown).

@@

```{r,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: tab-one
library(here)
library(dplyr)
library(knitr)
#subway_data_raw <- read.csv(file = '/Users/lucas/Documents/paper2/Subway_Ridership_V4.csv')
subway_data_raw <- read.csv(file = '/Users/xiuzh/Desktop/readingcourse/paper2/Subway_Ridership_V4.csv')

subway_data<-subway_data_raw%>%select(Country, Urbanname, Year, Ridership)

@@

```{r ,fig.width= 8,fig.height= 10,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-four
#| fig-cap: "Number of Turbine Manufacturers by Country"
library(readxl)
raw_pm10<-read_excel("/Users/lucas/Documents/paper2/aap_pm_database_may2014.xls", sheet="countries")
raw_pm10$`Annual mean, ug/m3...3`<-as.numeric(as.character(raw_pm10$`Annual mean, ug/m3...3`))
raw_pm10$Year...4<-as.numeric(as.character(raw_pm10$Year...4))
pm10<-raw_pm10%>%select(...2,`Annual mean, ug/m3...3`, Year...4)%>%filter(!is.na(...2))
colnames(pm10)<-c("Country", "PM10 Annual mean, ug/m3","Year")

@@

```{r ,fig.width= 15,fig.height= 20,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-five
#| fig-cap: "Number of Turbine Manufacturers by Country"

>>>>

## Analysis Tool
The data will be presented clearly and succinctly with these visuals, making it simpler to comprehend the relation between air pollution and subway. This following analysis is processed in R @R  with packages of tidyverse(@tidyverse), dplyr(@dplyr). The tables is constructed via knitr(@knite). The package inside of tidyverse helps to create the plots via ggplot2(@tidyverse). This paper is knitted as PDF file by the packages of R markdown (@RMarkdown).

@@

```{r,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: tab-one
library(here)
library(dplyr)
library(knitr)
subway_data_raw <- read.csv(file = '/Users/lucas/Documents/paper2/Subway_Ridership_V4.csv')
#subway_data_raw <- read.csv(file = '/Users/xiuzh/Desktop/readingcourse/paper2/Subway_Ridership_V4.csv')

subway_data<-subway_data_raw%>%select(Country, Urbanname, Year, Ridership,ReferencePeriod,Month)

@@

```{r ,fig.width= 8,fig.height= 10,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-four
#| fig-cap: "pm10"
library(readxl)
raw_pm10<-read_excel("/Users/lucas/Documents/paper2/aap_pm_database_may2014.xls", sheet="countries")
raw_pm10$`Annual mean, ug/m3...3`<-as.numeric(as.character(raw_pm10$`Annual mean, ug/m3...3`))
raw_pm10$Year...4<-as.numeric(as.character(raw_pm10$Year...4))
pm10<-raw_pm10%>%select(...2,`Annual mean, ug/m3...3`, Year...4)%>%filter(!is.na(...2))
colnames(pm10)<-c("Country", "PM10 Annual mean, ug/m3","Year")

@@

```{r ,fig.width= 15,fig.height= 20,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-five
#| fig-cap: "Relation by year"
